DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-12-05 2015CompleteDerivation/completeDerivation.tex
Complete rewrite of complex vector space justification

\subsection{Homogeneous decomposable systems and real vector spaces}
The notion that a system is decomposable means the states are equipped with a rule of composition that allows one to write $\mathcal{c}=\mathcal{c}_1+\mathcal{c}_2$: the composite system is the sum of its parts. For example, the state of a ball is equal to the state of its top and bottom parts.

@@

It is time to turn these concepts into a precise mathematical formulation following the template used for classical mechanics. We want to formalize the state space for an \emph{irreducible material} as a quantum particle will be a finite amount of such material.

As for the classical material, the irreducible material is thought to be decomposable: each state can be seen as the sum of different components (e.g. spatially distributed parts) such that the evolution of the whole is the composition of their evolution. Therefore \ref{prop:abelian_group} applies and the state space $\Psi$ of an irreducible material is an abelian group.

Note, though, that the components are in general not independent. As the motion of each fragment is statistical in nature, it will combine as statistical variables do. Suppose $X$ and $Y$ are two random variables,
\begin{equation}\label{eqn:correlation}
\sigma^2_{X+Y} = \sigma^2_{X} + \sigma^2_{Y} + 2 \, \sigma_{X} \sigma_{Y} \rho_{X,Y}
\end{equation}
where $\sigma^2$ is the variance, $\sigma$ is the standard deviation, and $\rho_{X,Y}=COV(X,Y)/\sigma_{X} \sigma_{Y}$ is the Pearson correlation coefficient. As $-1\leq\rho_{X,Y}\leq+1$, the total variance can be greater or smaller than the sum of the variance of the components. The strength of the chaotic motion of the fragments is something physically distinguishable as it contributes to the spread of the distribution. Therefore while the motion of each fragment is not itself physically distinguishable, it falls within the unstated part, the strength and correlation of the chaotic motion must be, they fall within the state.

How can we characterize the aspects of the unstated part that are captured by the state? We can look at the classical derivation for guidance. In that case, we looked at the set of transformations that increase/decrease the amount of material. We can think of them as the transformations that change the unstated part of the system. As the classical material is homogeneous, permutations between classical particles in the same state $\mathcal{s}$ do not matter (i.e. the ordering is unstated). Increasing/decreasing the amount of material increases/decreases the number of permutations and therefore changes the unstated part of the system. For the irreducible material we follow the same strategy: we look for the transformations that affect the unstated part while keeping the overall state, the distribution, unchanged.

Suppose we have $\psi_1$ a state for an amount $a_m$ of irreducible material characterized by one d.o.f. The material will be spread over the configurations of the infinitesimal fragments. As the material is homogeneous, it is spread evenly among such possible configurations. Counting fragment configurations is therefore equivalent to counting the amount of material. Each fragment would be identified by a pair of independent random variables $(A, B)$, as a d.o.f. is two-dimensional. The shape of the distribution and the actual values are not physically distinguishable: these are just dummy variables we assign to count the fragments. We can choose A and B to be uniform distributions of interval $\sqrt{a_m}$, so that they identify a square of area $a_m$, the amount of material.

Suppose we have another configuration $\psi_2$, where only the unstated part is changed. The unstated part of $\psi_2$ can also be characterized by a square formed by two independent uniform distributions (C, D). Counting states on (C,D) is equivalent to counting them on (A,B), as they are simply different arrangements of fragments within the same state. The relationship between the two pairs of variables must be linear since all distributions are uniform. That is: $C=aA+bB$ and $D= -bA + aB$. We can write $\psi_2 = \tau(a,b) \psi_1$ as $a$ and $b$ are the only parameters of the transformation. Or more compactly, $\psi_2 = \tau(c) \psi_1$ where $c=a+\imath b$.

The transformation $\tau(c)$ increases/decreases the area by the modulus $|c|^2=a^2+b^2$, which physically corresponds to the increase/decrease of amount of material. It also rotates the square by the phase $\theta_c \equiv arg(c) = arctan(a/b)$, which corresponds to a change in correlation: if $\theta_c = 0$, $C = |c| A$ are clearly correlated while if $\theta_c = \pi$, $C = - |c| A$ are clearly anti-correlated.

To better understand the link between phase and correlation, suppose $\psi$ is the state for an irreducible material. We can write $\tau(c) \psi = \tau(c_1 + c_2) \psi = \tau(c_1) \psi + \tau(c_2) \psi$ as the composition of two separate transformations. We have
\begin{equation}\label{eqn:correlation_state}
|c|^2=|c_1|^2 + |c_2|^2 + 2 |c_1||c_2|\cos(\theta_{c_2} - \theta_{c_1})
\end{equation}
Compare to \ref{eqn:correlation}. The material is spread evenly among fragment configurations. Also, since it is homogeneous, the ratio of fragments per configuration is the same. Therefore the amount of material is proportional to the strength of the chaotic motion of the fragment, which is measured by the variance. The increase/decrease in amount of material therefore combines like the variance of a statistical variable. The cosine of the phase difference takes the place of the Pearson correlation coefficient. A more meaningful name for the phase, then, would be \emph{correlation angle}. Also note how correlation for a single variable is a meaningless quantity: it is the correlation between two random variables that is significant. That is why in quantum mechanics phase differences have physical meaning, as it gives the correlation between two states, while absolute phases do not.

If we increase the number of independent d.o.f. the group of transformations remains the same.  As the material is homogeneous, the same amount of material needs to be spread over the same number of fragment configurations along each independent d.o.f. This means that, as we combine components, the strength of the chaotic motion has to be the same in all directions. This means that the increase/decrease of material and the change in correlation has to be the same across all d.o.f.

Mathematically, the state space $\Psi$ for an irreducible material is a complex vector space. It is so because it is the state space for a decomposable material (i.e. an abelian group) where we can increase/decrease the amount and change the correlation of the internal stochastic motion (i.e. a set of transformations conveniently parametrized by a complex number).

@@

	We claim the set of physically distinguishable transformations $T$ that change the unstated part of an irreducible material is isomorphic to $\mathbbm{C}$. Consider an amount $a_m \in \mathbbm{R}$ of irreducible material characterized by one d.o.f. The configuration of a fragment of the material is characterized by two random variables $A, B: \Omega \rightarrow \mathbbm{R}$ where $\Omega$ is the sample space for the configuration of the fragments. As the configuration of each fragment is physically indistinguishable, $A$ and $B$ can be chosen such that the distribution $\rho$ of material over such variables is uniform over a range of $\sqrt{a_m}$ for both variables. We have $a_m=\int \rho dA \wedge dB = \int dA \wedge dB$. Consider a second amount $\hat{a}_m$ of irreducible material in the same state. It also can be characterized by a uniform distribution over two variables $C, D: \Omega \rightarrow \mathbbm{R}$ over a range of $\sqrt{\hat{a}_m}$. As the two amounts of material are in the same state, $(C,D)$ is a function of $(A,B)$. We have $\hat{a}_m = \int dC \wedge dD = \int |J| dA \wedge dB$ where $|J|$ is the Jacobian determinant. As both distributions are uniform, $|J|$ has to be constant. The transformation has to be linear: $C=aA + bB$ and $D=-bA + aB$. As the change in amount of material, the only physically distinguishable quantity associated with the fragments, is fully specified by $a$ and $b$, no other transformation is physically relevant. Let $\tau: \mathbbm{C} \rightarrow T$ represent such a transformation parametrized by $c=a+\imath b$. $|c|^2 = |J| = (a^2 + b^2) = \hat{a}_m / a_m$ is the ratio of the two amounts of materials and is physically distinguishable. Define on $T$ an addition $+: T \times T \rightarrow T$ and a multiplication $*: T \times T \rightarrow T$ such that $\tau(a) + \tau(b) = \tau(a+b)$ and $\tau(a) * \tau(b) = \tau(a*b)$, $a,b \in \mathbbm{C}$, the sum and product of the transformation is equal to the sum and product of their respective factors. The phase $arg(c)$ under addition is physically distinguishable as it can affect the modulus of the result. $\tau$ is an isomorphism between $T$ and $\mathbbm{C}$ as fields. Assume now that the material is characterized by multiple independent d.o.f. The transformation on each d.o.f. is defined independently by $c_i \in \mathbbm{C}$. As $\hat{a}_m / a_m$ is the same under all d.o.f. $|c_i|=|c_j|$. The relationship has to always hold under addition as well, therefore $arg(c_i) = arg(c_j)$. $T\cong \mathbbm{C}$ also for multiple d.o.f.

@@

As each state $\psi$ can be identified by a wave function on either space, there must be an operator $\Upsilon^q_{\hat{q}}(\psi(q)) = \psi(\hat{q})$ that converts the wave function on one space to the other.\footnote{Note that a neighbourhood of $q^i$ is not necesserily a neighbourood of $\hat{q}^i$. They are only if $q^i$ and $\hat{q}^i$ can be expressed as a bijection of each other $\hat{q}^i(q^i)$: they are different coordinates of the same manifold.} As to a linear combination of states corresponds a linear combination of wave functions, $\Upsilon^q_{\hat{q}}$ is a linear operator. As converting the space again must give us the original wave function, $\Upsilon^{\hat{q}}_{q} \Upsilon^q_{\hat{q}}= 1$ is unitary. We can now define a have linear operator $F_{[\hat{q}^i]}$ corresponding to state variable $f : \hat{\mathcal{Q}} \rightarrow \mathbbm{R}$. Using $\Upsilon^{q}_{\hat{q}}$ we can express $F_{[q^i]} = \Upsilon^{\hat{q}}_{q} F_{[\hat{q}^i]} \Upsilon^{q}_{\hat{q}}$ as an operator over complex functions of $\mathcal{Q}$. It will be still be linear and hermitian.

@@

	We claim that for any fragment variable $f$ there exists a corresponding self-adjoint linear operator $F_{[q^i]} : \Psi(\mathcal{Q}, dq^i) \rightarrow C(\mathcal{Q}, \mathbbm{C})$ such that $\int \psi^\dagger(q^i) F_{[q^i]}( \psi(q^i)) d^nq$ is, if it exists, the expectation of $f$ multiplied by the amount of material. Let $f$ be a fragment variable. There exist a corresponding self-adjoint linear operator $F_{[\hat{q}^i]} : \Psi(\hat{\mathcal{Q}}, d\hat{q}^i) \rightarrow C(\hat{\mathcal{Q}}, \mathbbm{C})$ where $\hat{\mathcal{Q}}$ provides a maximal description. As both $\hat{\mathcal{Q}}$ and $\mathcal{Q}$ provide a maximal description, we can define $\Upsilon^{q^i}_{\hat{q}^i} \equiv \Upsilon_{\hat{q}^i} \circ \Upsilon_{q^i}^{-1}$ which transforms a wave function over $\mathcal{Q}$ into a wave function over $\hat{\mathcal{Q}}$. $\Upsilon^{q^i}_{\hat{q}^i}$ is an isomorphism as $\Upsilon_{\hat{q}^i}$ and $\Upsilon_{q^i}$ are isomorphisms. $\Upsilon^{q^i}_{\hat{q}^i}$ is unitary as $\Upsilon^{\hat{q}^i}_{q^i} \circ \Upsilon^{q^i}_{\hat{q}^i} = (\Upsilon^{q^i}_{\hat{q}^i})^{-1} \circ \Upsilon^{q^i}_{\hat{q}^i} = 1$. We can extend $\Upsilon^{q^i}_{\hat{q}^i}$ on all continuous functions and define $F_{[q^i]} \equiv \Upsilon^{\hat{q}^i}_{q^i} \circ F_{[\hat{q}^i]} \circ \Upsilon^{q^i}_{\hat{q}^i}$. $F_{[q^i]}$ is a self-adjoint linear operator. $\int \psi^\dagger(q^i) F_{[q^i]}( \psi(q^i)) d^nq = \int \psi^\dagger(\hat{q}^i) F_{[\hat{q}^i]}( \psi(\hat{q}^i)) d^n \hat{q}$ is, if it exists, the expectation of $f$ multiplied by the amount of material.

>>>>

\subsection{Homogeneous decomposable systems and vector spaces}
The notion that a system is decomposable means the states are equipped with a rule of composition that allows one to write $\mathcal{c}=\mathcal{c}_1+\mathcal{c}_2$: the composite system is the sum of its parts. For example, the state of a ball is equal to the state of its top and bottom parts.

@@

It is time to turn these concepts into a precise mathematical formulation as we did for classical mechanics. We want to formalize the state space for an \emph{irreducible material} as a quantum particle will be a finite amount of such material.

As for the classical material, the irreducible material is thought to be decomposable: each amount can be seen as the sum of different components (e.g. spatially distributed). Therefore \ref{prop:abelian_group} applies and the state space $\Psi$ of an irreducible material is an abelian group.

Yet, the description of each component cannot be more accurate than the description of the whole. To capture this idea precisely we need to characterize the aspects of the unstated part that influence the state definition. How do we do that? We can look at the classical derivation for guidance. In that case, we looked at the set of transformations that increased/decreased the amount of material. The idea is that we can think of these transformations as characterizing what the state can and cannot say about the infinitesimal parts.

Suppose we have a state $\mathcal{c}_1$ for an amount $a_m$ of classical material. Suppose we assigned a numeric identifier to each particle of the material. This identifier would be just a dummy label we assign, not a physically quantity. As the classical material is homogeneous, permutations between classical particles within the same state have no effect. Therefore the ordering given by the identifier does not matter. Identifying a classical particle within a composite state is equivalent to picking a number from a random variable $A$ uniformly distributed over an interval of size $a_m$.

Suppose we have another state $\mathcal{c}_2 = \tau(a) \mathcal{c}_1$ where the only difference is an increase/decrease of the amount of material by a factor $a$. The random variable $B$ that identifies a particle of $\mathcal{c}_2$ is now a uniform distribution $B=aA$ where the range is the new amount of material: there are now proportionally more/less labels to assign. This is also the only possible transformation that can link the two uniform random variables $A$ and $B$. Therefore increase/decrease of material is the only operation that is going to affect the labeling of the fragments that is captured by the state. In other words: the classical state does not care about the permutation of the fragments, but it cares how many fragments are there.

For the irreducible material we follow the same strategy and study the transformations that affect the labeling of what the irreducible state cannot tell us: the configuration of each fragment. Similarly, the irreducible state will not care about permutations of fragment configurations, but it will care how many fragment configurations are there.

Suppose we have a state $\psi_1$ for an amount $a_m$ of irreducible material characterized by one d.o.f. The configurations of the infinitesimal fragments will be identified by two values, as a d.o.f. is two-dimensional. Each fragment configuration is identified by a pair of independent random variables $(A, B)$, which are, as before, just dummy variables we use to name the fragment configurations. As the material is homogeneous, the distribution is uniform or we could tell something about the fragment configurations. We choose A and B to be uniform distributions of interval $\sqrt{a_m}$: identifying a fragment configuration is like picking a point at random over a square of area $a_m$, the amount of material.

Suppose we have another state $\psi_2$, where the labeling for the fragment configurations has changed. We can label the fragment configurations of $\psi_2$ in the same way, with two independent uniform distributions $(C, D)$. But since the labeling is the only thing that has changed, we must be able to relate the new distribution over $(C,D)$ to the old distribution over $(A,B)$. The relationship between the two pairs of variables must be linear since all distributions are uniform. $C=aA+bB$. To preserve the square distribution we must then have $D= -bA + aB$. We can write $\psi_2 = \tau(a,b) \psi_1$ as $a$ and $b$ are the only parameters of the transformation. Or more compactly, $\psi_2 = \tau(c) \psi_1$ where $c=a+\imath b$.

The transformation $\tau(c)$ increases/decreases the area by the modulus $|c|^2=a^2+b^2$, which physically corresponds to the increase/decrease of amount of material. It also rotates the square by the phase $\theta_c \equiv arg(c)$, which corresponds to a change in correlation: if $\theta_c = 0$, $C = |c| A$ are clearly correlated while if $\theta_c = \pi$, $C = - |c| A$ are clearly anti-correlated.

This line of reasoning is fairly abstract and it may seem to have no bearing with quantum states. Therefore, jumping a bit ahead, let's see if we can already find quantitative consequences of this model and see whether they are consistent with our knowledge of quantum mechanics.

If the amount of material is connected to the area of two uniform distributions, it should combine like the variance of a random variable. And in fact it does. Suppose $X$ and $Y$ are two random variables,
\begin{equation}\label{eqn:correlation}
\sigma^2_{X+Y} = \sigma^2_{X} + \sigma^2_{Y} + 2 \, \sigma_{X} \sigma_{Y} \rho_{X,Y}
\end{equation}
where $\sigma^2$ is the variance, $\sigma$ is the standard deviation, and $\rho_{X,Y}=COV(X,Y)/\sigma_{X} \sigma_{Y}$ is the Pearson correlation coefficient. As $-1\leq\rho_{X,Y}\leq+1$, the total variance can be greater or smaller than the sum of the variance of the components. Now suppose $\psi$ is the state for a unit amount of irreducible material (i.e. a quantum particle). We can write $c \psi = (c_1 + c_2) \psi = c_1 \psi + c_2 \psi$. We have:
\begin{equation}\label{eqn:correlation_state}
|c_1+c_2|^2=|c_1|^2 + |c_2|^2 + 2 |c_1||c_2|\cos(\theta_{c_2} - \theta_{c_1})
\end{equation}
The two expressions are formally identical and it shouldn't come as a surprise. The more material we have, the more labels for the fragment configurations to choose from. $-1\leq\cos(\theta_{c_2} - \theta_{c_1})\leq+1$ takes the place of the Pearson correlation coefficient. Quantum interference can then be understood in terms of the combination of correlated/anti-correlated distributions.

If the phase determines the correlation between two states, then it should only be meaningful when comparing two states. And in fact only differences in phases are physically distinguishable in quantum mechanics. A more meaningful name for the phase, then, would be \emph{correlation angle}.

If quantum states are uniform distributions over fragment configurations, we should see a hint of that when computing distributions over observables. And in fact we do. Suppose we have $Q\psi = q \psi$, an eigenstate of some observable. Then it is also an eigenstate of the infinitesimal transformation of the conjugate variable $1+\frac{Qdp}{\imath\hbar}$. Since it has a symmetry over $p$, the distribution is uniform on that parameter.

If quantum particle states are really just unit amount of material uniformly distributed, we should be able to calculate the Shannon entropy associated with them. Using our dummy variables $I(\psi_i) = - \int \rho ln (\rho) dA dB = - \int 1 ln (1) dA dB = 0$. For a quantum mixed state $\tilde{\rho} = \sum \tilde{\rho}_i |\psi_i\rangle \langle \psi_i |$, we have $I(\tilde{\rho}) = - \sum \tilde{\rho}_i ln \tilde{\rho}_i - \tilde{\rho}_i I(\psi_i) = - \sum \tilde{\rho}_i ln \tilde{\rho}_i = -tr(\tilde{\rho} ln \tilde{\rho})$. And in fact this is the Von Neumann entropy used in quantum information, that implicitly assumes all states provide the same amount of entropy (i.e. zero).

If two quantum particle states $\psi_1$ and $\psi_2$ are really just two states at equilibrium with the same entropy, we should always be able to find a deterministic and reversible evolution to connect the two. And in fact we can. Take the plane identified by $\psi_1$ and $\psi_2$. Find the infinitesimal rotation $1 + \frac{Od\alpha}{\imath\hbar}$ along that plane. $\psi_2 = e^{\frac{O\alpha}{\imath\hbar}} \psi_1$ is the unitary evolution of the other. Note that this is \emph{not} always possible in classical mechanics, as two states $\mathcal{c}_1$ and $\mathcal{c}_2$ may have different entropy.

In other words, not only our simple model is consistent, but it has predictive power: it provides intuition that is well supported by these findings. It is not ``just a mathematical trick".

If we increase the number of independent d.o.f. the group of transformations remains the same. While we have more fragment configurations to label, each d.o.f. is labeled independently. Therefore we have $n$ uniform distributions, each over a square of the same amount of material. This means that, as we combine components, the labels have to combine in the same way along the different d.o.f.: the increase/decrease of material and the change in correlation has to be the same across all d.o.f.

Mathematically, the state space $\Psi$ for an irreducible material is a complex vector space. It is so because it is the state space for a decomposable material (i.e. an abelian group) where we can increase/decrease the amount and change the correlation of the internal description (i.e. a set of transformations conveniently parametrized by a complex number).

@@

	We claim the set of physically distinguishable transformations $T$ that change the unstated part of an irreducible material is isomorphic to $\mathbbm{C}$. Consider an amount $a_m \in \mathbbm{R}$ of irreducible material characterized by one d.o.f. The configuration of a fragment of the material is characterized by two random variables $A, B: \Omega \rightarrow \mathbbm{R}$ where $\Omega$ is the sample space for the configuration of the fragments. As the material is homogeneous, $A$ and $B$ can be chosen such that the distribution $\rho$ of material over such variables is uniform over a range of $\sqrt{a_m}$ for both variables. We have $a_m=\int \rho dA \wedge dB = \int dA \wedge dB$. Consider a second amount $\hat{a}_m$ of irreducible material in the same state. Its fragment configurations can also be characterized by a uniform distribution over two variables $C, D: \Omega \rightarrow \mathbbm{R}$ over a range of $\sqrt{\hat{a}_m}$. As the two amounts of material are in the same state, $(C,D)$ is a function of $(A,B)$. We have $\hat{a}_m = \int dC \wedge dD = \int |J| dA \wedge dB$ where $|J|$ is the Jacobian determinant. As both distributions are uniform, $|J|$ has to be constant. The transformation has to be linear: $C=aA + bB$ and $D=-bA + aB$. As the change in amount of material, the only physically distinguishable quantity associated with the fragment configurations, is fully specified by $a$ and $b$, no other transformation is physically relevant for the state. Let $\tau: \mathbbm{C} \rightarrow T$ represent such a transformation parametrized by $c=a+\imath b$. $|c|^2 = |J| = (a^2 + b^2) = \hat{a}_m / a_m$ is the ratio of the two amounts of materials and is physically distinguishable. Define on $T$ an addition $+: T \times T \rightarrow T$ and a multiplication $*: T \times T \rightarrow T$ such that $\tau(a) + \tau(b) = \tau(a+b)$ and $\tau(a) * \tau(b) = \tau(a*b)$, $a,b \in \mathbbm{C}$, the sum and product of the transformation is equal to the sum and product of their respective factors. The phase $arg(c)$ under addition is physically distinguishable as it can affect the modulus of the result. $\tau$ is an isomorphism between $T$ and $\mathbbm{C}$ as fields. Assume now that the material is characterized by multiple independent d.o.f. The transformation on each d.o.f. is defined independently by $c_i \in \mathbbm{C}$. As $\hat{a}_m / a_m$ is the same under all d.o.f. $|c_i|=|c_j|$. The relationship has to always hold under addition as well, therefore $arg(c_i) = arg(c_j)$. $T\cong \mathbbm{C}$ also for multiple d.o.f.

@@

As each state $\psi$ can be identified by a wave function on either space, there must be an operator $\Upsilon^q_{\hat{q}}(\psi(q)) = \psi(\hat{q})$ that converts the wave function on one space to the other.\footnote{Note that a neighbourhood of $q^i$ is not necesserily a neighbourood of $\hat{q}^i$. They are only if $q^i$ and $\hat{q}^i$ can be expressed as a bijection of each other $\hat{q}^i(q^i)$: they are different coordinates of the same manifold.} As to a linear combination of states corresponds a linear combination of wave functions, $\Upsilon^q_{\hat{q}}$ is a linear operator. As converting the space again must give us the original wave function, $\Upsilon^{\hat{q}}_{q} \Upsilon^q_{\hat{q}}= I$ is unitary. We can now define a have linear operator $F_{[\hat{q}^i]}$ corresponding to state variable $f : \hat{\mathcal{Q}} \rightarrow \mathbbm{R}$. Using $\Upsilon^{q}_{\hat{q}}$ we can express $F_{[q^i]} = \Upsilon^{\hat{q}}_{q} F_{[\hat{q}^i]} \Upsilon^{q}_{\hat{q}}$ as an operator over complex functions of $\mathcal{Q}$. It will be still be linear and hermitian.

@@

	We claim that for any fragment variable $f$ there exists a corresponding self-adjoint linear operator $F_{[q^i]} : \Psi(\mathcal{Q}, dq^i) \rightarrow C(\mathcal{Q}, \mathbbm{C})$ such that $\int \psi^\dagger(q^i) F_{[q^i]}( \psi(q^i)) d^nq$ is, if it exists, the expectation of $f$ multiplied by the amount of material. Let $f$ be a fragment variable. There exist a corresponding self-adjoint linear operator $F_{[\hat{q}^i]} : \Psi(\hat{\mathcal{Q}}, d\hat{q}^i) \rightarrow C(\hat{\mathcal{Q}}, \mathbbm{C})$ where $\hat{\mathcal{Q}}$ provides a maximal description. As both $\hat{\mathcal{Q}}$ and $\mathcal{Q}$ provide a maximal description, we can define $\Upsilon^{q^i}_{\hat{q}^i} \equiv \Upsilon_{\hat{q}^i} \circ \Upsilon_{q^i}^{-1}$ which transforms a wave function over $\mathcal{Q}$ into a wave function over $\hat{\mathcal{Q}}$. $\Upsilon^{q^i}_{\hat{q}^i}$ is an isomorphism as $\Upsilon_{\hat{q}^i}$ and $\Upsilon_{q^i}$ are isomorphisms. $\Upsilon^{q^i}_{\hat{q}^i}$ is unitary as $\Upsilon^{\hat{q}^i}_{q^i} \circ \Upsilon^{q^i}_{\hat{q}^i} = (\Upsilon^{q^i}_{\hat{q}^i})^{-1} \circ \Upsilon^{q^i}_{\hat{q}^i} = I$. We can extend $\Upsilon^{q^i}_{\hat{q}^i}$ on all continuous functions and define $F_{[q^i]} \equiv \Upsilon^{\hat{q}^i}_{q^i} \circ F_{[\hat{q}^i]} \circ \Upsilon^{q^i}_{\hat{q}^i}$. $F_{[q^i]}$ is a self-adjoint linear operator. $\int \psi^\dagger(q^i) F_{[q^i]}( \psi(q^i)) d^nq = \int \psi^\dagger(\hat{q}^i) F_{[\hat{q}^i]}( \psi(\hat{q}^i)) d^n \hat{q}$ is, if it exists, the expectation of $f$ multiplied by the amount of material.
